{\large Master Thesis}\\{\normalsize on

### 2011-07-20 doc/report.tex
m

% TODOs
% skarpere plots
% sørg for at figurer ikke sidder underligt
% Prøv at formindske for store mellemrum mellem ord ved at lave påtvungne linjeskift
% hav plot for $r=\sqrt n$ med til forsvar

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.5\textwidth,page=1]{resultspace.pdf}
    \end{center}
    \caption{\label{fig:resultspace-empty}The result space for $LCE_s(i,j)$ for $1 \leq i < j \leq n$ where $s = abacbbacbacacabc$.}
\end{figure}

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.5\textwidth,page=2]{resultspace.pdf}
    \end{center}
    \caption{\label{fig:resultspace-directcomp}$LCE(3,7)$ using \proc{DirectComp}.}
\end{figure}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.5\textwidth,page=3]{resultspace.pdf}
    \end{center}
    \caption{\label{fig:resultspace-t-row}$LCE(3,7)$ with distance $t=4$ between each stored row.}
\end{figure}

@@

\begin{lemma}
The preprocessing algorithm described above takes $O(\sortt + k\cdot n)$ time.
\end{lemma}

\begin{proof}
We first construct the SA and LCP arrays, which takes $O(\sortt)$ time~\cite{sort-complexity}. We then preprocess each of the $k$ levels in $O(n)$ time, since we loop through $n$ substrings, and comparing neighboring substrings takes constant time when we use the LCE array. The total preprocessing time becomes $O(\sortt\\ + k\cdot n)$.
\end{proof}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-alla.plt}
    \end{center}
    \caption{\label{fig:plot-rmq}Query times of \proc{LcpRmq} using different variants of RMQ.}
\end{figure}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-directcomp-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-directcomp-alla.plt}
    \end{center}
    \caption{\label{fig:plot-rmq-directcomp}Query times of constant time \proc{LcpRmq}, \proc{DirectComp} and \proc{DirectComp+LcpRmq}.}
\end{figure}

@@

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-complookup-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-complookup-alla.plt}
    \end{center}
    \caption{\label{fig:plot-complookup}Query times of our new DirectCompLookup algorithm versus the existing \proc{DirectComp} and \proc{LcpRmq} algorithms.}
\end{figure}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-2l-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-2l-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-tval}Query times of \fprint[2] for different values of $t_1$ versus query times for \proc{DirectComp}.}
\end{figure}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avglog-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avglog-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-avglog}Query times of \fprint[\logceil] with $O(1)$ versus $O(k)$ average case query time.}
\end{figure}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avg3l-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avg3l-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-avg3l}Query times of \fprint[3] with $O(1)$ versus $O(k)$ average case query time.}
\end{figure}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-alla.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-repeat-pow.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-rand2.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-cache-horiz}Query times of \fprint[2] with and without intra-level cache optimization.}
\end{figure}

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-log-cache-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-log-cache-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-cache-vert}Query times of \fprint[2] with and without inter-level cache optimization.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ziv-Lempel Compression\label{sec:lz-compress}}

@@

@@

The \proc{HeavyPathLce} data structure consists of the following:
\begin{itemize}
\item An input tree $T$ with a heavy path decomposition.
\item A string $s$, which is a concatenation of strings of all heavy paths of $T$, where the string of a heavy path is the label of the light edge leading to the heavy path concatenated with the label of the heavy path. \pref{fig:tree-heavy-ds} shows an example of $s$.
\item For a node $u$, $\zend(u)$ points to the node of greatest depth in $u$'s heavy path, $d(u)$ is the depth of $u$, and $\zindex(u)$ is the index in $s$, which stores $\zlabel(u)$.
\item Data structures for constant time NCA on $T$, constant time LA on $T$, and constant time LCE on $s$.
\end{itemize}

@@

We have looked at applying \proc{SuffixNca} and \proc{LcpRmq} directly to trees like we did with \proc{DirectComp} and \fprintk, such that we can get $O(1)$ query time.

>>>>

% TODOs
% skarpere plots
% sørg for at figurer ikke sidder underligt
% Prøv at formindske for store mellemrum mellem ord ved at lave påtvungne linjeskift

% hav plot for $r=\sqrt n$ med til forsvar

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.42\textwidth,page=1]{resultspace.pdf}
    \end{center}
    \caption{\label{fig:resultspace-empty}The result space for $LCE_s(i,j)$ for $1 \leq i < j \leq n$ where $s = abacbbacbacacabc$.}
\end{figure}

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.42\textwidth,page=2]{resultspace.pdf}
    \end{center}
    \caption{\label{fig:resultspace-directcomp}$LCE(3,7)$ using \proc{DirectComp}.}
\end{figure}

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.42\textwidth,page=3]{resultspace.pdf}
    \end{center}
    \caption{\label{fig:resultspace-t-row}$LCE(3,7)$ with distance $t=4$ between each stored row.}
\end{figure}

@@

@@

\begin{samepage}
\begin{lemma}
The preprocessing algorithm described above takes $O(\sortt + k\cdot n)$ time.
\end{lemma}
\begin{proof}
We first construct the SA and LCP arrays, which takes $O(\sortt)$ time~\cite{sort-complexity}. We then preprocess each of the $k$ levels in $O(n)$ time, since we loop through $n$ substrings, and comparing neighboring substrings takes constant time when we use the LCE array. The total preprocessing time becomes $O(\sortt\\ + k\cdot n)$.
\end{proof}
\end{samepage}

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-alla.plt}
    \end{center}
    \caption{\label{fig:plot-rmq}Query times of \proc{LcpRmq} using different variants of RMQ.}
\end{figure}

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-directcomp-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-rmq-directcomp-alla.plt}
    \end{center}
    \caption{\label{fig:plot-rmq-directcomp}Query times of constant time \proc{LcpRmq}, \proc{DirectComp} and \proc{DirectComp+LcpRmq}.}
\end{figure}

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-complookup-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-complookup-alla.plt}
    \end{center}
    \caption{\label{fig:plot-complookup}Query times of our new DirectCompLookup algorithm versus the existing \proc{DirectComp} and \proc{LcpRmq} algorithms.}
\end{figure}

@@

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-2l-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-2l-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-tval}Query times of \fprint[2] for different values of $t_1$ versus query times for \proc{DirectComp}.}
\end{figure}

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avglog-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avglog-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-avglog}Query times of \fprint[\logceil] with $O(1)$ versus $O(k)$ average case query time.}
\end{figure}

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avg3l-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-avg3l-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-avg3l}Query times of \fprint[3] with $O(1)$ versus $O(k)$ average case query time.}
\end{figure}

@@

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-alla.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-repeat-pow.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-cache-rand2.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-cache-horiz}Query times of \fprint[2] with and without intra-level cache optimization.}
\end{figure}

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-log-cache-rand10.plt}
        \includegraphics[width=0.49\textwidth,type=pdf,ext=.pdf,read=.pdf]{../src/results/length-fingerprint-log-cache-alla.plt}
    \end{center}
    \caption{\label{fig:plot-fingerprint-cache-vert}Query times of \fprint[2] with and without inter-level cache optimization.}
\end{figure}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Ziv-Lempel Compression\label{sec:lz-compress}}

@@

\begin{samepage}
\subsubsection{Data Structure}

@@

The \proc{HeavyPathLce} data structure consists of the following:
\begin{itemize}
\item An input tree $T$ with a heavy path decomposition.
\item A string $s$, which is a concatenation of strings of all heavy paths of $T$, where the string of a heavy path is the label of the light edge leading to the heavy path concatenated with the label of the heavy path. \pref{fig:tree-heavy-ds} shows an example of $s$.
\item For a node $u$, $\zend(u)$ points to the node of greatest depth in $u$'s heavy path, $d(u)$ is the depth of $u$, and $\zindex(u)$ is the index in $s$, which stores $\zlabel(u)$.
\item Data structures for constant time NCA on $T$, constant time LA on $T$, and constant time LCE on $s$.
\end{itemize}
\end{samepage}

@@

We have looked at applying \proc{SuffixNca} and \proc{LcpRmq} directly to trees like we did with \proc{DirectComp} and \fprintk, to get $O(1)$ query time.
